Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-26 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex After meet with Andy, but not completely updated what we discussed...

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\NewDocumentEnvironment{compare}{}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
\NewDocumentEnvironment{oldText}{m}{#1{The following is old text.}\noindent\begin{minipage}[t]{1\columnwidth}}{#1{The old text end here.}\end{minipage}\newpage}
\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[t]{1\columnwidth}#1{The following is new text.}}{\end{minipage}#1{The new text end here.}}

@@

Our approach, based on QIVPMs, introduces the concept of $\delta$-determinism,
where~$\delta$ quantifies the effect of finite-precision uncertainties
on measurement outcomes.  Our parameter $\delta$ is not necessarily
related to the description of states; we are agnostic about
attributing elements of reality to the state function. Instead, we
attribute lack of certainty to the uncertain results obtained through
the use of a measuring instrument.  Thus, the parameter~$\delta$ in
our framework reflects insufficient knowledge of the experimenter,
which could be due to a variety of reasons related to imperfections of
devices. For example, a typical question that an experimenter may not
be able to answer accurately would be ``did an electron land in the
left half or the right half of the screen?''  There are cases in which
the electron would land too close to the middle of the screen for the
experimenter to be able to determine with certainty that it was left
or right of the center.  We simply record this imprecision by
generalizing the probabilities assigned to events to intervals of
uncertainties.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution.

We next introduce probability axioms for IVPMs. First, for each
interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability interval for impossible events and events
that are certain. We can write this, respectively, as
$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$
is the empty set and $\Omega$ is the event covering the entire sample
space.  For each interval $[\ell,r]$, we also need the dual interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event~$E$, the dual refers to the probability of the event's
complement $\overline{E}$.  For example, if we discover as a result of
an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu\left(\overline{E}\right)=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately so the combined event should be mapped to
a sharper interval. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu\left(\overline{E}\right)\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint enforcing coherence of
the probability assignment for
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is therefore:
\begin{equation}
\label{eq:disjoint}
\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,.
\end{equation}
Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)\cup\mu\left(\overline{E}\right)$.
%% Parallel arguments
%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
%% essential new information seems to be introduced.

@@

\begin{definition}[QIVPM]\label{def:QIVPM}
  Assume a collection of intervals $\mathscr{I}$ including $\imposs$
  and $\necess$ with addition and scalar multiplication defined as
  follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
   &  & \bar{\mu}(\mathbb{1})=\necess\,,\label{eq:necess}\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess-\bar{\mu}\left(P\right)\,,\label{eq:complement}
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors~$P_0$
  and~$P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures.

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\cite{TaiThesis2018}. A
consequence of this fact is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.

We now give the necessary technical definitions to prove this
non-empty core property. We say a QIVPM $\bar{\mu}$ is
\emph{consistent} with a state $\rho$ and a projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with classical probability spaces, there is \emph{no
guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.

We next refine the concept of consistency by introducing the idea of
a ``core'' set of states relative to subspaces. First, we define
$\events'$ as a \emph{subspace} of a set of events if $\events$ if
$\events'$ contains  $\mathbb{0}$ and $\mathbb{1}$ and is closed under
complements, sums, and products.  In particular, for any
projector~$P\in\events'$, we have
$\mathbb{1}-P\in\events'$ and for each pair of commuting
projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.

@@

To see this idea in the context of a quantum experiment, consider
a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
to build a probability measure that maps every projection to either
$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
defined in Table~\ref{tab:probability-measures} is not a QIVPM.

>>>>

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\NewDocumentEnvironment{compare}{}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
\NewDocumentEnvironment{oldText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is old text.}}{#1{The old text end here.}\end{minipage}\newpage}
\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is new text.}}{#1{The new text end here.}\end{minipage}}

@@

Our approach, based on QIVPMs, introduces the concept of $\delta$-determinism,
where~$\delta$ quantifies the effect of finite-precision uncertainties
on measurement outcomes.  Our parameter $\delta$ is not necessarily
related to the description of states; we are agnostic about
attributing elements of reality to the state function. Instead, we
attribute lack of certainty to the uncertain results obtained through
the use of a measuring instrument.  Thus, the parameter~$\delta$ in
our framework reflects insufficient knowledge of the experimenter,
which could be due to a variety of reasons related to imperfections of
devices. For example, a typical question that an experimenter may not
be able to answer accurately would be ``did an electron land in the
left half or the right half of the screen?''  There are cases in which
the electron would land too close to the middle of the screen for the
experimenter to be able to determine with certainty that it was left
or right of the center.  We simply record this imprecision by
generalizing the probabilities assigned to events to intervals reflecting the
uncertainties.

@@

We will start by reviewing classical IVPMs and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution.

We next introduce probability axioms for IVPMs. First, for each
interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals that
refer, respectively, to the probability interval for impossible events and
for events that are certain. We can write the latter as
$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$
is the empty set and $\Omega$ is the event covering the entire sample
space.  For each interval $[\ell,r]$, we also need the dual interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event~$E$, the dual refers to the probability of the event's
complement $\overline{E}$.  For example, if we discover as a result of
an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu\left(\overline{E}\right)=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately so the combined event should be mapped to
a sharper interval. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu\left(\overline{E}\right)\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint enforcing coherence of
the probability assignment for
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is taken to be:
\begin{equation}
\label{eq:disjoint}
\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,.
\end{equation}
Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)\cup\mu\left(\overline{E}\right)$.
%% Parallel arguments
%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
%% essential new information seems to be introduced.

@@

\begin{definition}[QIVPM]\label{def:QIVPM}
  Assume a collection of intervals $\mathscr{I}$ including $\imposs$
  and $\necess$ with addition and scalar multiplication defined as
  follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}\label{eq:interval-times}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
   &  & \bar{\mu}(\mathbb{1})=\necess\,,\label{eq:necess}\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess-\bar{\mu}\left(P\right)\,,\label{eq:complement}
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors~$P_0$
  and~$P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}

\begin{compare}
\begin{oldText}{\andy}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures. 
\end{oldText}
\begin{newText}{\andy}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
intervals appearing in Eq.~(\ref{eq:interval-times})
is a natural consequence of the minus sign appearing in
Eq.~(\ref{eq:complement}).}  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
aspects of both classical IVPMs and quantum probability measures.
\end{newText}
\end{compare}

\begin{compare}
\begin{oldText}{\andy}
Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\cite{TaiThesis2018}. A
consequence {\color{blue}of this fact} is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if {\color{blue}the set of events is} mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.
\end{oldText}
\begin{newText}{\andy}
Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\cite{TaiThesis2018}. A
consequence is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if {\color{blue}we restrict ourselves to the set
$\eventsC$ of} mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.
\end{newText}
\end{compare}

We now give the necessary technical definitions to prove this
non-empty core property.
\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and a projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .\label{eq:consistent}
  \end{equation}
In contrast with classical probability spaces, there is \emph{no
guarantee} that there exists a unique state $\rho$ that satisfies
Eq.~(\ref{eq:consistent}) and therefor is consistent with a QIVPM.
\end{definition}

We next refine the concept of consistency by introducing the idea of
a ``core'' set of states relative to subspaces. First, we define
$\events'$ as a \emph{subspace} of a set of events if $\events$ if
$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed
under complements, sums, and products.  In particular, for any
projector~$P\in\events'$, we have
$\mathbb{1}-P\in\events'$ and for each pair of commuting
projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.

@@

To see this idea in the context of a quantum experiment, consider
a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
that is repeated $12$ times. By the Kochen-Specker theorem, it is impossible
to build a probability measure that maps every projection to either
$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
defined in Table~\ref{tab:probability-measures} is not a QIVPM.
